European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-21 manuscript/manuscript.qmd
add execute options
Add results table to manuscript (#11)
plus move table sizing to qmd from PCA.R

* add execute options

* move resizing to demo

* add unresized regtable.rdata

* Add results table to manuscript

---
title: European or American? A re-examination of the transatlantic influence over the IMF
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
---

@@

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
execute:
  echo: false
  warning: false
  error: false
  message: false
---

@@

```{r results}
#| label: tbl-results
#| tbl-cap: Comparative Effects of US and EU Influence on IMF Lending Outcomes (1980–2010)
#| tbl-pos: H
load('save/regTable.RData')
resultsTable |> tinytable::theme_tt("resize", width = 1)
```
